%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% Primordial Machine's Math Scalars Library
% Copyright (C) 2017-2019 Michael Heilmann
%
% This software is provided 'as-is', without any express or implied warranty.
% In no event will the authors be held liable for any damages arising from the
% use of this software.
%
% Permission is granted to anyone to use this software for any purpose,
% including commercial applications, and to alter it and redistribute it
% freely, subject to the following restrictions:
%
% 1. The origin of this software must not be misrepresented;
%    you must not claim that you wrote the original software.
%    If you use this software in a product, an acknowledgment
%    in the product documentation would be appreciated but is not required.
%
% 2. Altered source versions must be plainly marked as such,
%    and must not be misrepresented as being the original software.
%
% 3. This notice may not be removed or altered from any source distribution.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\documentclass[oneside]{book}

\input{common}

\SetOrganization{Primordial Machine's}
\SetLibraryName{Math Scalars Library}

\SetLibraryIncludeFileName{include.hpp}
\SetLibraryIncludesDirectoryPath{primordialmachine/math-scalars/\newline\$(PlatformTarget.toLower())/\$(Configuration.toLower())/includes}

\SetLibraryIncludeDirectiveFilePath{primordialmachine/math/scalars/include.hpp}

\SetLibraryStaticLibrariesDirectoryPath{primordialmachine/math/scalars/\newline\$(PlatformTarget.toLower())/\$(Configuration.toLower())/libraries}
\SetLibraryStaticLibraryFileName{math-scalars.lib}

\SetLibraryVersion{v1.0}
\SetLibraryRepository{https://github.com/primordialmachine/math-scalars}
\SetAuthor{Michael Heilmann}
\SetEmail{michaelheilmann@primordialmachine.com}

\SetDocumentType{User Manual}

\begin{document}

\frontmatter

\begin{titlepage}
\maketitle
\end{titlepage}

\tableofcontents
\addtocontents{toc}{\protect\thispagestyle{empty}}
\pagenumbering{gobble}

\mainmatter

\chapter{Synopsis}
C++ 17 library providing floating point scalars.
The library is made available publicly on
\href{\GetLibraryRepository}{Github}
under the
\href{\GetLibraryRepository/blob/master/LICENSE}{MIT License}.

\chapter{Limitations and Restrictions}
The library officially only supports Visual Studio 2017 and Windows 10.

\chapter{Introductory example}
\textit{\color{orange}This library does not provide any examples yet.}
%Examples are located in the \href{\GetLibraryRepository/blob/master/examples}{examples} directory.

\input{building_visual_studio_2017}

\chapter{Library Interface Documentation}

\section{\texttt{namespace primordialmachine}}
The namespace this library is adding its declarations/definitions to.
The added namespace elements are documented below.

\section{\textit{Scalar} (type concept)}
A \textit{Scalar} type is a type \texttt{S} which provides support for the following operators\newline
\texttt{
S operator*( S, S );\newline
S operator/( S, S );\newline
S operator+( S, S );\newline
S operator-( S, S );\newline
\newline
S\& operator*=( S\&, S );\newline
S\& operator/=( S\&, S );\newline
S\& operator+=( S\&, S );\newline
S\& operator-=( S\&, S );\newline
\newline
bool operator==( S, S );\newline
bool operator!=( S, S );\newline
bool operator<=( S, S );\newline
bool operator< ( S, S );\newline
bool operator>=( S, S );\newline
bool operator> ( S, S );}

\section{\texttt{is\_scalar} (struct)}
This template defines a compile-time boolean constant value which can be used to
determine whether a type \texttt{TYPE} is a valid scalar type. It must        be
specialized in order to introduce a user-defined scalar type to       Primordial
Machine's mathemmatical libraries. Such types must satisfy the            scalar
requirements.

\noindent\texttt{template \textlangle typename TYPE\textrangle\newline
struct is\_scalar \{\newline
\hspace*{2em}static constexpr bool value = false;\newline
\};}

\noindent{}This library provides specializations for all floating point    types
where \texttt{value} is \texttt{true}.

\end{document}
